Perihelion advance of Mercury

### 2020-09-25 perihelion_advance_of_mercury.Rmd
use cache for time consuming calculations

```{r,label=orbitsimulatorGRlongtime,cache=TRUE}
out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e16,len=1e7))
```

@@

```{r,precessionwithclassicaldynamics,cache=TRUE}
out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e16,len=1e7),GR=FALSE)
jj1 <- c(NA,out$rdot)
jj2 <- c(out$rdot,NA)
change <- (jj1>0) & (jj2<0)
tee    <- out$time[change]
phi <- out$phi[change]
phi <- (phi) %% (2*pi)
plot(tee,phi-pi,main='orbital angle at of Mercury at perihelion, classical case',xlab='time (seconds)',ylab='angle of perihelion')
```

>>>>

```{r,label=orbitsimulatorGRlongtime,cache=TRUE}  # takes ~5 mins to run
out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e16,len=1e7))
```

@@

```{r,precessionwithclassicaldynamics,cache=TRUE}  # takes ~ 5 mins to run
out <- trajectory(merc_perihelion, m=d, h=h, tau=seq(from=0,to=35e16,len=1e7),GR=FALSE)
jj1 <- c(NA,out$rdot)
jj2 <- c(out$rdot,NA)
change <- (jj1>0) & (jj2<0)
tee    <- out$time[change]
phi <- out$phi[change]
phi <- (phi) %% (2*pi)
plot(tee,phi-pi,main='orbital angle at of Mercury at perihelion, classical case',xlab='time (seconds)',ylab='angle of perihelion')
```
